Same as always: I suck at titles

### 2024-09-27 manuscript/manuscript_eb.Rmd
changes & version sent for feedback

keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
wordcount         : "4774"

@@

We modelled participants' betting behaviour in a linear mixed model. We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded. The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction. The maximal model [@barretal2013], with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge. We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept. The final model included a random intercept by-item. Results were deemed significant at |t| > 2 [@baayen2008].

@@

Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`). There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and no other significances (for speaker, `r mdlbet_m1_all$full_result$speaker_cont1`; for the interaction `r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].

@@

Table \@ref(tab:tab5) depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.  Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score. For the _Affect_ dimension, we reverse-scored items measuring negative affect. Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`). We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.

@@

Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours. This second model improved model fit ($\chi^2$(6) = 19.46, _p_ < .01). Besides a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (`r mdlbet_attitudes$full_result$affect`)

@@

@@

The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions. This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2020; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015]. This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.

@@

Overall,

>>>>

keywords          : "filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing"
wordcount         : "5173"

@@

We modelled participants' betting behaviour in a linear mixed model. We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded. The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction. The maximal model [@barretal2013], with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge. We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept. The final model included a random intercept by-item.

@@

Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (`r mdlbet_m1$full_result$delivery_cont1`). There was no main effect of speaker (`r mdlbet_m1$full_result$speaker_cont1`) and importantly, no interaction between manner of delivery and speaker (`r mdlbet_m1$full_result$delivery_cont1_speaker_cont1`)^[An identical model including excluded participants showed a main effect of fluency (`r mdlbet_m1_all$full_result$delivery_cont1`), and a main effect for speaker (`r mdlbet_m1_all$full_result$speaker_cont1`), but no significant interaction (`r mdlbet_m1_all$full_result$delivery_cont1_speaker_cont1`)].

@@

Table \@ref(tab:tab5) depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background.  Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score. For the _Affect_ dimension, we reverse-scored items measuring negative affect. Cronbach's alpha showed that the scores for these attitudes were reliable ($\alpha_{affect}$ = `r affect_alpha`, $\alpha_{status}$ = `r status_alpha`, $\alpha_{solidarity}$ = `r solidarity_alpha`). We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for _p_ values.

@@

Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours. This second model improved model fit ($\chi^2$(7) = 24.77, _p_ < .01). The model showed a main effect of manner of delivery (`r mdlbet_attitudes$full_result$delivery_cont1`). Although affect (`r mdlbet_attitudes$full_result$affect`) and fluency (`r mdlbet_attitudes$full_result$fluent`) were significant, they did not survive Bonferroni correction.

@@

Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery. A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour (`r mdlbet_m1_exposure$full_results$exposure`)

@@

The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions. This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension [e.g., @boskeretal2014; @arnoldetal2007; @helleretal2015], and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations [e.g., @fairchildetal2020; @lorenzonietal2022; @ippapafragou2022; @fairchildpapafragou2018] possibly because native listeners expect them to produce those [@levari2015]. This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.

@@

Overall, our study shows that disfluency is a cue that listeners take as an index of speaker's knowledgeability. Importantly, in situations of uncertainty where individuals lack information to optimise their behaviour, the presence of disfluency biases their otherwise rational behaviour. This highlights individuals' tuning to the different ways in which a speaker's mental state is signalled in speech and how in turn it can affect their subsequent behaviours.

### 2024-09-27 manuscript/manuscript_eb.tex
changes & version sent for feedback

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 4774}
\usepackage{lineno}

@@

We modelled participants' betting behaviour in a linear mixed model. We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded. The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction. The maximal model (Barr, Levy, Scheepers, \& Tily, 2013), with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge. We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept. The final model included a random intercept by-item. Results were deemed significant at \textbar t\textbar{} \textgreater{} 2 (Baayen, 2008).

Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)). There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t = -3.99\)), and no other significances (for speaker, \(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t = 1.15\); for the interaction \(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t = 1.28\))}.

@@

Table \ref{tab:tab5} depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background. Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score. For the \emph{Affect} dimension, we reverse-scored items measuring negative affect. Cronbach's alpha showed that the scores for these attitudes were reliable (\(\alpha_{affect}\) = 0.80, \(\alpha_{status}\) = 0.93, \(\alpha_{solidarity}\) = 0.87). We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.

@@

\begin{tabular}{lll}
\toprule
Dimension & \multicolumn{1}{c}{Native Speaker} & \multicolumn{1}{c}{Non-native Speaker}\\
\midrule
Comprehensibility & 7.62 (1.57) & 5.51 (2.14)\\
Accentedness & 5.46 (2.1) & 6.84 (1.37)\\
Affect & 5.77 (1.49) & 6.05 (1.32)\\
Status & 5.95 (1.52) & 6.43 (1.31)\\
Solidarity & 5.67 (1.48) & 6.41 (1.24)\\
Trustworthy & 6 (1.61) & 6.36 (1.41)\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llll}
\toprule
Dimension & \multicolumn{1}{c}{t(359)} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{d}\\
\midrule
Comprehensibility & 15.99 & {}[1.85, 2.36] & 2.11\\
Accent & -11.51 & {}[-1.62, -1.15] & -1.39\\
Affect & -3.54 & {}[-0.44, -0.13] & -0.29\\
Status & -6.55 & {}[-0.62, -0.33] & -0.48\\
Solidarity & -9.63 & {}[-0.89, -0.59] & -0.74\\
Trustworthy & -4.12 & {}[-0.53, -0.19] & -0.36\\
\bottomrule
\end{tabular}

@@

Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours. This second model improved model fit (\(\chi^2\)(6) = 19.46, \emph{p} \textless{} .01). Besides a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t = -4.02\)), the model showed an effect of affect, whereby higher ratings of affect were more likely to yield higher bettings (\(\hat{\beta} = 0.81\), 95\% CI \([0.14, 1.49]\), \(t = 2.35\))

@@

@@

The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions. This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; \textbf{lorenzonietal2020?}) possibly because native listeners expect them to produce those (Lev-Ari, 2015). This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.

@@

\leavevmode\vadjust pre{\hypertarget{ref-baayen2008}{}}%
Baayen, R. H. (2008). \emph{Analyzing linguistic data: A practical introduction to statistics using r}. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511801686}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5173}
\usepackage{lineno}

@@

We modelled participants' betting behaviour in a linear mixed model. We modelled money bet on each horse, taken from the final amounts submitted in the experiment, after all four descriptions had been heard and valid responses (summing to at most 100 pounds) had been recorded. The model included fixed effects of fluency (sum-coded; fluent coded as -0.5, disfluent as +0.5), speaker's linguistic background (sum-coded, native coded as -0.5; non-native coded as +0.5), and their interaction. The maximal model (Barr, Levy, Scheepers, \& Tily, 2013), with random intercepts by-participant and by-item, with random slopes for fluency and speaker's linguistic background by-participant, and for fluency by-item, failed to converge. We first dropped the random intercept by-participant, as most participants used all the money and thus there was no variance in their intercept. The final model included a random intercept by-item.

Our model showed a main effect of fluency, whereby participants placed lower bets following disfluent descriptions compared to their fluent counterparts (\(\hat{\beta} = -2.71\), 95\% CI \([-4.04, -1.38]\), \(t(1433) = -3.99\), \(p < .001\)). There was no main effect of speaker (\(\hat{\beta} = 0.78\), 95\% CI \([-0.55, 2.11]\), \(t(1433) = 1.15\), \(p = .251\)) and importantly, no interaction between manner of delivery and speaker (\(\hat{\beta} = 1.74\), 95\% CI \([-0.92, 4.40]\), \(t(1433) = 1.28\), \(p = .200\))\footnote{An identical model including excluded participants showed a main effect of fluency (\(\hat{\beta} = -2.92\), 95\% CI \([-3.91, -1.92]\), \(t(2557.08) = -5.75\), \(p < .001\)), and a main effect for speaker (\(\hat{\beta} = 1.21\), 95\% CI \([0.21, 2.20]\), \(t(2557.09) = 2.38\), \(p = .017\)), but no significant interaction (\(\hat{\beta} = 0.93\), 95\% CI \([-1.06, 2.92]\), \(t(2557.12) = 0.92\), \(p = .358\))}.

@@

Table \ref{tab:tab5} depicts the means (and standard deviation) of ratings in each of the measures of interest by speaker's linguistic background. Constructs measured with more than one question (affect, status, solidarity) were obtained by calculating the average score. For the \emph{Affect} dimension, we reverse-scored items measuring negative affect. Cronbach's alpha showed that the scores for these attitudes were reliable (\(\alpha_{affect}\) = 0.80, \(\alpha_{status}\) = 0.93, \(\alpha_{solidarity}\) = 0.87). We explored differences between evaluations of the native and the non-native speaker in these three social dimensions as well as on Comprehensibility, Accentedness, Fluency, and Trustworthiness via paired t-test using Bonferroni correction for \emph{p} values.

@@

\begin{tabular}{lll}
\toprule
Dimension & \multicolumn{1}{c}{Native Speaker} & \multicolumn{1}{c}{Non-native Speaker}\\
\midrule
Comprehensibility & 7.62 (1.57) & 5.51 (2.14)\\
Accentedness & 5.46 (2.1) & 6.84 (1.37)\\
Fluency & 7.97 (1.43) & 6.11 (1.83)\\
Affect & 5.77 (1.49) & 6.05 (1.32)\\
Status & 5.95 (1.52) & 6.43 (1.31)\\
Solidarity & 5.67 (1.48) & 6.41 (1.24)\\
Trustworthy & 6 (1.61) & 6.36 (1.41)\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llll}
\toprule
Dimension & \multicolumn{1}{c}{t(359)} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{d}\\
\midrule
Comprehensibility & 15.99 & {}[1.85, 2.36] & 2.11\\
Accent & -11.51 & {}[-1.62, -1.15] & -1.39\\
Fluency & 17.15 & {}[1.65, 2.08] & 1.87\\
Affect & -3.54 & {}[-0.44, -0.13] & -0.29\\
Status & -6.55 & {}[-0.62, -0.33] & -0.48\\
Solidarity & -9.63 & {}[-0.89, -0.59] & -0.74\\
Trustworthy & -4.12 & {}[-0.53, -0.19] & -0.36\\
\bottomrule
\end{tabular}

@@

Following our pre-registered analysis, we included these six variables in our previous model to explore whether speakers' evaluations could further explain participants' betting behaviours. This second model improved model fit (\(\chi^2\)(7) = 24.77, \emph{p} \textless{} .01). The model showed a main effect of manner of delivery (\(\hat{\beta} = -2.71\), 95\% CI \([-4.03, -1.39]\), \(t(1436.00) = -4.03\), \(p < .001\)). Although affect (\(\hat{\beta} = 0.83\), 95\% CI \([0.15, 1.50]\), \(t(1436.09) = 2.41\), \(p = .016\)) and fluency (\(\hat{\beta} = -0.67\), 95\% CI \([-1.24, -0.10]\), \(t(1436.10) = -2.31\), \(p = .021\)) were significant, they did not survive Bonferroni correction.

@@

Following previous research suggesting the role of exposure to foreign-accented speech in its role to trust and comprehensibility, we explored whether exposure to native and non-native speakers played a role in participants' betting behaviour beyond that of speaker identity and manner of delivery. A similar linear mixed model to that employed in our main analysis, but with the addition of exposure, showed that it did not affect participants' betting behaviour ()

@@

The fact that disfluencies could also be accounted for by speaker's nativeness did not impact participants' decisions. This pattern differs from what we predicted given previous research suggesting that stereotypes about speaker's linguistic abilities have consequences for whether and how disfluencies affect speech comprehension (Arnold et al., 2007; e.g., Bosker, Quené, Sanders, \& De Jong, 2014; Heller et al., 2015), and the fact that errors produced by non-native speakers are less likely to trigger otherwise negative interpretations (e.g., Fairchild et al., 2020; Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni et al., 2022) possibly because native listeners expect them to produce those (Lev-Ari, 2015). This is particularly remarkable given that in our post-experimental questionnaire, the native speaker was more likely to be chosen as someone participants would like to learn from about horse races in the future.

@@
